\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistatic control of gene expression in Humans\\[0.3cm] \huge *** Report V1 *** \\ \horrule{2pt} \\[0.5cm]

### 2013-05-14 docs/manuscript/report_v1.tex
minor changes to the report
included some tables and figure on the replication analysis

@@

%%% Refs
\bibliographystyle{plain}
\bibliography{report_v1_refs}

>>>>

\subsection{Replication}

Replication in Fehrmann and EGCUT

Of the 432 probe by SNP pair associations supplied to the replication group(s) 387 and 391 were present at the desired criteria in Fehrmenn and EGCUT respectively.

\begin{table}[ht]
	\centering
	\begin{tabular}{rrrr}
	\hline
	& & Fehrmann & EGCUT \\
	\hline
	P value & Expected & Observed & Observed \\
	\hline	  
	0.1 & 38 & 51 & 67 \\
	0.05 & 19 & 35 & 44 \\
	0.01 & 4 & 22 & 26 \\
	0.001 & <1 & 14 & 22 \\
	0.0001 & ~0 & 7 & 17 \\
	\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrllrlrrrrr}
  \hline
chr1 & chr2 & pos1 & pos2 & snp1 & snp2 & probechr & probegene & snpcor & replication\_pnest & replication\_r & replication\_nclass & replication\_minclass \\ 
  \hline
19 &  19 & 483171 & 483155 & rs807491 & rs7254601 &  19 & TMEM149 & 0.02 & 81.55 & 0.05 &   9 &  16 \\ 
19 &  19 & 481151 & 481145 & rs873870 & rs7252981 &  19 & ATP13A1 & -0.26 & 48.72 & -0.34 &   9 &  12 \\ 
11 &  11 & 345268 & 345257 & rs7930237 & rs556895 &  11 & CTSC & -0.11 & 18.76 & 0.09 &   9 &   8 \\ 
10 &  10 & 317649 & 317615 & rs2395095 & rs10824092 &  10 & ADK & 0.12 & 18.33 & 0.10 &   9 &  13 \\ 
8 &   8 & 277063 & 277044 & rs2123758 & rs3889129 &   8 & NAPRT1 & 0.23 & 15.12 & 0.18 &   9 &  34 \\ 
3 &   3 & 110710 & 110699 & rs16864367 & rs13069559 &   3 & MBNL1 & 0.29 & 10.30 & 0.23 &   9 &   9 \\ 
14 &   3 & 416822 & 110699 & rs2614467 & rs13069559 &   3 & MBNL1 & -0.02 & 4.13 & 0.03 &   9 &  12 \\ 
19 &   8 & 483165 & 252775 & rs8106959 & rs1843357 &  19 & TMEM149 & 0.02 & 3.72 & -0.00 &   9 &  10 \\ 
19 &   3 & 483165 & 117001 & rs8106959 & rs10937361 &  19 & TMEM149 & 0.01 & 3.61 & -0.00 &   9 &  12 \\ 
8 &   3 & 257325 & 117283 & rs8180944 & rs4553956 &   8 & HMBOX1 & 0.05 & 3.38 & -0.05 &   9 &   4 \\ 
19 &   1 & 483165 & 38950 & rs8106959 & rs914940 &  19 & TMEM149 & 0.04 & 3.36 & -0.05 &   9 &   8 \\ 
19 &   2 & 483165 & 80806 & rs8106959 & rs6718480 &  19 & TMEM149 & 0.02 & 3.31 & -0.02 &   9 &  10 \\ 
19 &   6 & 483165 & 216524 & rs8106959 & rs6926382 &  19 & TMEM149 & -0.05 & 3.06 & -0.03 &   9 &  12 \\ 
19 &  14 & 483165 & 414535 & rs8106959 & rs17719594 &  19 & TMEM149 & 0.04 & 3.06 & 0.02 &   9 &  12 \\ 
5 &   3 & 155373 & 110699 & rs7710738 & rs13069559 &   3 & MBNL1 & 0.10 & 2.55 & -0.03 &   9 &   9 \\ 
19 &  12 & 483165 & 379273 & rs8106959 & rs1401098 &  19 & TMEM149 & -0.01 & 2.41 & 0.04 &   9 &  11 \\ 
17 &  15 & 450341 & 430903 & rs1533031 & rs12591171 &  17 & XAF1 & -0.04 & 2.38 & -0.03 &   9 &   9 \\ 
14 &   8 & 406922 & 265704 & rs7152284 & rs2896452 &   8 & C8ORF59 & 0.02 & 2.18 & 0.07 &   9 &  17 \\ 
19 &   5 & 483884 & 178750 & rs4803481 & rs2421050 &  19 & CEACAM21 & 0.07 & 2.16 & -0.02 &   9 &   9 \\ 
7 &   1 & 242078 & 11854 & rs12532999 & rs12065581 &   1 & GPR177 & -0.08 & 2.13 & 0.04 &   9 &  10 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrllrlrrrrr}
  \hline
chr1 & chr2 & pos1 & pos2 & snp1 & snp2 & probechr & probegene & snpcor & replication\_pnest & replication\_r & replication\_nclass & replication\_minclass \\ 
  \hline
19 &  19 & 483171 & 483155 & rs807491 & rs7254601 &  19 & TMEM149 & 0.02 & 45.78 & -0.13 &   9 &   3 \\ 
19 &  19 & 481151 & 481145 & rs873870 & rs7252981 &  19 & ATP13A1 & -0.26 & 42.37 & 0.37 &   9 &   3 \\ 
10 &  10 & 317649 & 317615 & rs2395095 & rs10824092 &  10 & ADK & 0.12 & 21.21 & -0.04 &   9 &  11 \\ 
3 &   3 & 110710 & 110699 & rs16864367 & rs13069559 &   3 & MBNL1 & 0.29 & 20.36 & 0.18 &   9 &   4 \\ 
8 &   8 & 277063 & 277044 & rs2123758 & rs3889129 &   8 & NAPRT1 & 0.23 & 16.08 & 0.01 &   9 &  29 \\ 
11 &  11 & 345268 & 345257 & rs7930237 & rs556895 &  11 & CTSC & -0.11 & 15.06 & 0.19 &   9 &   2 \\ 
19 &   4 & 483165 & 137487 & rs8106959 & rs2351458 &  19 & TMEM149 & 0.03 & 9.61 & -0.02 &   9 &   4 \\ 
19 &   6 & 483165 & 216524 & rs8106959 & rs6926382 &  19 & TMEM149 & -0.05 & 8.80 & -0.03 &   9 &   6 \\ 
5 &   3 & 155373 & 110699 & rs7710738 & rs13069559 &   3 & MBNL1 & 0.10 & 7.89 & 0.05 &   9 &   4 \\ 
19 &   1 & 483165 & 38950 & rs8106959 & rs914940 &  19 & TMEM149 & 0.04 & 6.96 & 0.01 &   9 &   3 \\ 
17 &   3 & 450326 & 110699 & rs218671 & rs13069559 &   3 & MBNL1 & -0.03 & 5.82 & 0.00 &   9 &   4 \\ 
6 &   3 & 207083 & 110699 & rs2030926 & rs13069559 &   3 & MBNL1 & 0.05 & 5.80 & -0.00 &   9 &   1 \\ 
19 &  13 & 483165 & 380931 & rs8106959 & rs9509428 &  19 & TMEM149 & -0.01 & 5.75 & -0.01 &   9 &   2 \\ 
7 &   3 & 236869 & 110699 & rs11981513 & rs13069559 &   3 & MBNL1 & 0.02 & 5.36 & 0.00 &   9 &   5 \\ 
19 &   2 & 483165 & 80806 & rs8106959 & rs6718480 &  19 & TMEM149 & 0.02 & 5.15 & -0.07 &   9 &   1 \\ 
4 &   3 & 126893 & 110699 & rs4392535 & rs13069559 &   3 & MBNL1 & 0.02 & 4.33 & -0.02 &   9 &   1 \\ 
8 &   3 & 248082 & 110699 & rs4735830 & rs13069559 &   3 & MBNL1 & 0.03 & 4.21 & -0.05 &   9 &   4 \\ 
19 &  11 & 483165 & 353621 & rs8106959 & rs471728 &  19 & TMEM149 & 0.04 & 3.62 & 0.04 &   9 &   4 \\ 
19 &   8 & 483165 & 252775 & rs8106959 & rs1843357 &  19 & TMEM149 & 0.02 & 3.33 & -0.04 &   9 &   2 \\ 
19 &  17 & 483165 & 462278 & rs8106959 & rs7213338 &  19 & TMEM149 & 0.04 & 3.14 & 0.04 &   9 &   7 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}[p]
	\centering
	\includegraphics[width=15cm]{images/EGCUT_vs_Fehrmann_all}
	\caption{-log10 pvalues for all snp / probe pairs in Fehrnmann and EGCUT}
	\label{fig:repl_match}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=15cm]{images/EGCUT_vs_Fehrmann_pval10}
	\caption{-log10 pvalues for all snp / probe pairs with -log10 p values less than 10 in Fehrnmann and EGCUT datasets}
	\label{fig:repl_match10}
\end{figure}

@@

%%% Refs
\clearpage
\bibliographystyle{plain}
\bibliography{report_v1_refs}
